### 2015-04-20 ase-2015-tex/bisimulation.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

The bisimulation proof in this section establishes the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, any properties proven with~\gsetxt{}
can also be proved using the symbolic heap algorithm.~\gsetxt{} concretizes
the possible heap configurations along with various aliasing
relationships when an uninitialized field is dereferenced. The rules
for initializing and updating the fields in the Javalite semantics for
\gsetxt{} are shown in the~\appref{app:gse}.

>>>>

The bisimulation proof in this section establishes the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, any properties proven
with~\gsetxt{} can also be proved using the symbolic heap
algorithm.~\gsetxt{} concretizes the possible heap configurations
along with various aliasing relationships when an uninitialized field
is dereferenced. The rules for initializing and updating the fields in
the Javalite semantics for \gsetxt{} are shown in Appendix B where as
the the complete set of rules for the symbolic heap algorithm are
shown in Appendix C.

### 2015-04-20 ase-2015-tex/lazy.tex
Created ase-2015-tex folder, ported CAV paper to ASE format.

\section{Generalized Symbolic Execution}
\label{app:gse}
The specialization of Javalite to generalized symbolic execution with
lazy initialization using the summary heap is in \figref{fig:lazyInit}
for the initialization and \figref{fig:lazy} for how the
initialization is used. Specifically, the field-access rule in
\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
the accessed field is instantiated. Initialization in generalized
symbolic execution never happens for more than one object on any use
of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly one
location.

>>>>

\section{Generalized Symbolic Execution}
\label{app:gse}
The specialization of Javalite to generalized symbolic execution with
lazy initialization using the symbolic heap is in
\figref{fig:lazyInit} for the initialization and \figref{fig:lazy} for
how the initialization is used. Specifically, the field-access rule in
\figref{fig:lazy} uses initialization, $\rightarrow_I^*$, to be sure
the accessed field is instantiated. Initialization in generalized
symbolic execution never happens for more than one object on any use
of $\rightarrow_I^*$: $\Lambda$ is either empty or contains exactly
one location.
